---
title: "simpleRegress"
author: "Roxan Barakat"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```


```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

According to RSE (residual standard error),   

the #1 best model to predict length is "head length" with the lowest RSE of 4.235,  
the second best is "chest" with RSE of 4.939,  
the third best is "neck" with RSE of 5.376,  
the fourth best is "weight" with RSE of 5.376,  
the fifth best is "head width" with RSE of 7.32,   
and the worst is "age" with the highest RSE of 7.511.  

The order of the models from worst to best of predicting length other than neck is: age, head width, weight, chest, head length. 



